\documentclass[]{deedy-resume-openfont}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Aksh}{Chordia}{
\href{mailto:chordia.2@iitj.ac.in}{chordia.2@iitj.ac.in} | (+91) 9530200403\\ \href{https://www.linkedin.com/in/akshchordia}{LinkedIn/akshchordia} | \href{https://www.github.com/aakshjn}{Github.com/aakshjn}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.30\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{\large IIT JODHPUR}
\location{JODHPUR, INDIA}
\descript{Pre Final Year B.Tech in Electrical Engineering }
Expected \custombold{May 2021}\\
CGPA \custombold{7.8/10}\small(Upto 4th Sem.)\\
\sectionsep


\runsubsection{SAMRAT PUBLIC SCHOOL}
\descript{\large Class 12 | CBSE}
\location{AJMER, INDIA}
\location{Year \custombold{2017}}
\location{Percentage: \custombold{89.6}}

\sectionsep
\runsubsection{ST. STEPHEN'S SCHOOL}
\descript{\large {Class 10 | CBSE}}
\location{AJMER, INDIA }
\location{Year \custombold{2015}}
\location{CGPA \custombold{10/10}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{COURSEWORK} 
\textbullet{}Physics of Semiconductor\\ 
\hspace{4pt} Devices\\
\textbullet{}Basic Electrical Engineering\\
\textbullet{}Electromagnetic Theory\\
\textbullet{}Circuit Theory\\
\textbullet{}Signals And Systems\\
\textbullet{}Electrical Machines\\
\textbullet{}Power Systems\\
\textbullet{}Digital Logic and Design\\
\textbullet{}Power Electronics*\\
\textbullet{}Micro-controllers And\\
\hspace{6pt}Microprocessors*\\
\textbullet{}Analog Electronics*\\
**$Ongoing Courses$\\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\textbullet{}C/C++ \\
\textbullet{}Python\\
\textbullet{} Matlab\\ 
\textbullet{} Arduino IDE\\
\subsection{HDL}
 \textbullet{} Verilog\\
 \textbullet{} Xilinx Petalinux\\
 \textbullet{} Xilinx Vivado
\subsection{Embedded}
\textbullet{}8051 $\mu Controller$\\
\textbullet{} Keil $\mu$ Vision
\subsection{Utilities}
\textbullet{} Proteus ISIS \\
\textbullet{} GIT \textbullet{} SSH
\subsection{OTHER TECHNOLOGIES}
\textbullet{} Arduino\\
\textbullet{IFTTT}\\
\textbullet{}Node MCU\\
\textbullet{} Raspberry Pi\\
\textbullet{}Microsoft Azure

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.69\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{TVS MOTORS INDIA}
\descript{| SUMMER INTERN | \custombold{R\&D} }
\location{MAY 2019 - JULY 2019 | HOSUR, INDIA}
\vspace{\topsep}
\begin{tightemize}
\item Project: To develop adaptive headlights in 2 wheelers. 
\item Learned about various types of \custombold{Automotive Lighting technologies} in use and \\proposed a circuitry for the purpose.  
\end{tightemize}
\sectionsep

\runsubsection{TVS Motors INDIA}
\descript{| SUMMER INTERN| \custombold{R\&D} }
\location{MAY 2018 – JULY 2018 | HOSUR, INDIA}
\begin{tightemize}
\item Project: Development of a cooling system for \custombold{the lithium-ion battery} pack.
\item Identified various types of cooling methods and thermal Controller \\(\custombold{Battery Management System}) designs for the application.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROJECTS}
\runsubsection{BTech Project}
\descript{| \custombold{VLSI | IoT | FPGA}}
\location{Video \arrowlink{https://youtu.be/wWGfXN3OqWY}{\underline{Youtube}} | Open Sourced \arrowlink{https://github.com/aakshjn/Environment-monitor-with-vlsi}{\underline{Github}}}
\begin{tightemize}
\item Demonstrated \custombold{IoT solution for environmental monitoring} using \custombold{VLSI} over an \\\custombold{FPGA board.}
\item \custombold{DIGILENT's ZYBO FPGA} board acted as a bridge between the sensors, screen,\\ and cloud-server.
\end{tightemize}
\sectionsep


\runsubsection{DISASTER CHAIN}
\descript{| \custombold{IoT | MICROSOFT AXLE 2019 | MICROSOFT CODE.FUN.DO++}}
\location{Video \arrowlink{https://www.youtube.com/watch?v=_PcUHHltb04}{\underline{Youtube}}| Open-Sourced \arrowlink{https://github.com/anshulahuja98/Codefundo-18-IITJ}{\underline{Github}} | News Article \arrowlink{https://timesofindia.indiatimes.com/city/bengaluru/ai-iot-power-student-projects-to-manage-disasters/articleshow/67858079.cms}{\underline{TOI}}} 
\begin{tightemize}
\item A \custombold{distributed IoT based solution} for \custombold{disaster detection} and early warning\\
systems build for cloud offloading of disaster management.
\item It is built using \custombold{Raspberry Pi} and \custombold{NODE MCU} units, placed at different locations \\of a building.
\end{tightemize}
\sectionsep


\runsubsection{SMART TAP}
\descript{| \custombold{IoT| IICDC: TEXAS INSTRUMENTS' HACKATHON}}
\location{Aug 2018 – NOV 2018}
 \begin{tightemize}
\item An \custombold{IoT based system} to acquire the \custombold{real-time water-usage data} from taps and \\showers installed at public locations using \custombold{flow, conductivity, TDS and pH sensors.} \item The data acquired to be analyzed and provide feedback to the individuals.
\end{tightemize}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{AWARDS AND ACHIEVEMENTS} 
\begin{tabular}{rll}
2019    & \custombold{2\textsuperscript{nd} Runner up, Microsoft AXLE}(Code.Fun.Do++ National) out of 21 teams.\\
        & Prize money \custombold{1 Lach INR} and 5000 USD Azure Grant under AI for good initiative. \\
2018    & \custombold{Winner, Microsoft Code.Fun.Do++} campus challenge.\\
        & Won prize money \custombold{20K INR.}\\
2018    & \custombold{Bronze Winner,} Campus Sustainability and Innovation Challenge of Annual \\
        & \custombold{INTER-IIT Tech. Meet.}\\
2018    & Reached \custombold{3\textsuperscript{rd}} round of India Innovation Challenge 2018, by \custombold{Texas Instruments}. \\
        & for the project "\custombold{Smart Tap.}"\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Positions of Responsibility
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{POSITIONS OF RESPONSIBILITY} 
\vspace{10pt}
\begin{tightemize}
\item \custombold{CAPTAIN} | MAY 2019- Present | \custombold{Electronics Club,} IIT Jodhpur.\\
 \item \custombold{VICE-CAPTAIN} | MAY 2018- APR 2019 | \custombold{Electronics Club,} IIT Jodhpur.\\
 \end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Extracurriculars
\section{Extracurriculars}
\vspace{10pt}
\begin{tightemize}
    \item \custombold{Class Representative}| B-Tech. Electrical Engineering batch of '21 at IIT Jodhpur. 
    \item Organised Intra College Technical Fest-\custombold{Nimble 2019}.
    \item Conducted various talks on \custombold{Home automation, microcontrollers, RF technology.}
    \item Rank Holder of numerous National Level Science and Cyber \custombold{Olympiads}.
    \item An active member of IIT Jodhpur \custombold{football} team.
\end{tightemize}
\end{minipage} 
\end{document}  \documentclass[]{article}
